Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed quasars

### 2020-05-15 manuscript/manuscript.tex
Pull from Tommaso's edits

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed AGNs}

@@

% Abstract of the paper
\begin{abstract}
  One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution. The magnification of strongly lensed quasars provide a way to effectively increase instrumental resolution and thus overcome this challenge. In this work, we study eight strong lens systems with deep {\it Hubble Space Telescope}(\hst) imaging, using the state-of-the-art \lenstronomy\ code to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models. 
  \mbh\ are estimated from broad emission line using standard methods. Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolve over cosmic time.  At the moment, the \pink{sample size of lensed AGN is small and thus} provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN. However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and may become a key diagnostic of black hole and galaxy co-evolution. 
\end{abstract}

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt a the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
The broad line properties of our samples are \pink{mostly} adopted from the literature. % \citep{Sluse2012, Peng2006, Shen2011}.
\pink{For SDSS1206, the line properties have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literatures~\citep{Sluse2012, Peng2006} with lensing magnification effect considered. For HS2209, the spectrum data was observed from ESI in September 2015. We derived the line properties using the same approach as~\citep{Sluse2012}. \todo{Dominique and Chris can give more details here.} }. The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

@@

{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W. \pink{The multi-band imaging data provides us the opportunity to estimate the host color and derive an accurate stellar population. We adopted the lensing modelling approach as introduced in Section~\ref{sec:photometry} to infer the host photometry at F814W and F555W two bands. Based on the three band host magnitudes, we find a 1.5~Gyr age and solar metallicity stellar population could well match the color. More detailed information is presented in Appendix~\ref{app:HE0435}.}
%Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy. Thus, we infer the color of the lensed arcs in the image plane. Based a their magnitudes in three bands, we find a 1.5 Gyr stellar population with solar metallicity could well match this color. More detailed information is presented in Appendix~\ref{app:HE0435}.}

@@

\subsection{The \mbh-\mstar\ relation}\label{sec:relation}
In Figures~\ref{fig:scaling_relation}-(a) we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.  We expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget for the entire sample. Following D20, we adopt as baseline a local \mbh-\mstar\ of the form:
\begin{eqnarray}
\label{eq:MMlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}),
  \end {eqnarray}
\pink{with calibrated value as  $\alpha = 0.27$, $\beta = 0.98$ based on the 55 local sample.} We find that our lensed systems are above the local relation, consistent with the inference from the 32  non-lensed AGNs published by D20 in a  similar redshift range. To quantify the evolution as a function of redshift, we parameterize it as:
\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
\end{eqnarray} 
where the $\Delta \log \mathcal M_{\rm BH}$ is the offset of \mbh\ with respect to the local baseline at fixed \mstar. To make a direct comparison, we reproduce the plot shown in Figure~8 of D20. Then, we add our new lensed AGN measurement and show the result in Figure~\ref{fig:scaling_relation}-(b). We find that the offset from the local relationship is indistinguishable for the two samples. \pink{Based on Equation~\eqref{eq:offset}, we estimate the evolution of the eight lensed systems and obtain $\gamma=1.49\pm0.43$, which overlaps with D20's inference ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.} This consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20\pink{that the observed value of \mbh\ at a fixed \mstar\ tend to be larger at higher redshift than the ones in the local universe.}

\pink{The lensed AGN systems in this work are directly taken from the H0LiCOW collaboration. We note that selection function of our sample is irrelevant to D20's sample. Given that the eight lensed AGN sample is relatively a small size, in this work we only take them for consistency check with the previous studies. The selection effect of the lensed sample will be investigated when the volume of the lens systems is large enough with statistical significance.}

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar.pdf}}&
{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar_vz.pdf}}\\
\end{tabular}
\caption{\label{fig:scaling_relation} 
(left): BH masses vs. stellar mass correlation (\mbh-\mstar). The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval based on Equation~\ref{eq:MMlocal}.
(right): offset of $\log(\mathcal M_{\rm BH})$ (vs. \mstar) as a function of redshift. \pink{We plot our new measurements on top of the figure to make direct comparison. The red line and shaded region are the best-fit and $1-\sigma$ offset fitting by Equation~\eqref{eq:offset} using the 32 high-z AGNs in D20, while the blue line and region are the fitting based on the eight lensed systems.} \blue{[Xuheng: Let me know if your don't like the current plots.]}
}
\end{figure*}

@@

We considered set of modelling choices to perform the fitting and the final inference is based on a weighting of top ranked choices. In particular, we treat the two different modelling approaches, i.e., {\it noise boost} and {\it PSF iteration} equally, to derive the averaged results. Of course, the results are somewhat dependent on the weighting scheme. However, the dependency is smaller than other sources of uncertainty.  For example, the dispersion of the results by the top ranked choices and thus using different weighting schemes would only change the results marginally ($<0.1$~dex).

@@

\section{Conclusion}\label{sec:con}
Using eight strongly lensed AGN systems, we presented a new measurements of the correlations of the mass of supermassive black hole with the stellar masses of their host galaxy. We adopt state-of-the-art lens modelling techniques to estimate the magnitude host galaxy, in terms of a standard \sersic\ profile. We estimated the \mbh\ of our sample using a set of calibrated single-epoch estimators to assure self-consistency and consistency with the comparison samples taken from the literature.

We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the similar approaches to derive the \mstar\ and calibrated the \mbh\ using consistent recipes. The \mbh-\mstar\ correlation and its evolution with cosmic time is in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}. The consistent result by our sample confirms\pink{the conclusion of evolution of the D20 as follows. First of all, the growth of the supermassive black hole predates that of its host galaxy during their co-evolution. Besides, for the high-$z$ sample, it is the total stellar masses that are measured and compared. Note that the actual morphologies of these hosts could be more complicated, such as disk and bulge component (system RXJ1131 for example). However, the local sample are bulge-dominated galaxies and the entire local \mstar\ adopted is their bulge mass. If the high-$z$ sample could be all resolved to focus the comparison on the bulge, the compared \mstar\ would be smaller (i.e., disk mass removed). As a result, the inferred evolution for the \mbh-bulge relation would be much even stronger. Taken together, these results suggest a scenario in which the stellar mass is transferred from disk to the bulge at a faster rate than the growth of \mbh\ since $z\sim2$.}

Our work based on highly magnified AGN showcases the power of lensing to effectively increase the resolution of a telescope and shows that uncertainties related to lens modelling are subdominant with respect to other sources of uncertainty like black hole mass. Furthermore, our work provides a powerful verification of the fidelity of the host galaxy reconstruction in non-lensed AGN.

@@

\todo{Xuheng: Hi Tommaso please confirm if I cite the right reference including Treu2010, Auger2010, Tre++18, Ang++18, Lem++20}

@@

This work is based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. X.D., S.B., and T.T. acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T. \todo{To be updated.}

@@

\subsection{HE0435}\label{app:HE0435}
\pink{Besides WFC3/F160W, HE0435 has also been observed through bands ACS/F814W and ACS/F555W (GO-9744; PI: C. S. Kochanek). Our aim is to derive the brightness of the host galaxy through all the three band to investigate the color and stellar population in the image plane. We use the modelling approach introduced in Section~\ref{sec:photometry} to perform this inference for the F814W and F555W bands. To save computer time, we only use the {\it PSF iteration} approach. We also fix the lens mass slope value to 1.9 since it is closer the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}. The inference of the fittings are shown in Figure~\ref{fig:app_HE0435}-(a), (b). Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}} \todo{cite Morishita's paper if any.} to perform the SED fitting. The stellar population with 1.5 Gyr and solar metallicity could provide the best fitting to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c), which is finally taken to estimate th host stellar mass.}

\begin{figure*}
\centering
\subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}\\
\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/HE0435_host_color.pdf}}\\
\caption{\label{fig:app_HE0435} 
Illustrations of the inference of HE0435 using the multi-band data. Top two panels: best-fit model of the lensed arcs shown as Figure~\ref{fig:image_inference}. Bottom panel: SED inference. \pink{The red points with error are the inferred host flux at the three bands in the image plane}.}
\end{figure*}

@@

\subsection{WFI2033}\label{app:WFI2033}
\pink{In addition to the WFC3/F160W, WFI2033 has been observed by \hst\ in other four bands, including WFC3/F125W (GO-12874; PI: D. Floyd), WFC3/F140W (GO-13732; PI: A. Nierenberg), ACS/F555W+F814W  (GO-9744; PI: C. S. Kochanek). Similar to Section~\ref{app:HE0435}, the lens modelling and the host photometry of WFI2033 have been inferred through these four bands. The results are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d). Unfortunately, limited by its exposure time, the data quality through F125W is not ideal and the host information could not be well extracted. Thus, we does not take the inference by F125W into account in the SED fitting. Using four-band photometry, we find the stellar population of 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}-(e).}
\begin{figure*}
\centering
\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/WFI2033_host_color.pdf}}
\caption{\label{fig:app_WFI2033} 
Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. \pink{The inference of the host photometry is not clear using the F125W data, and thus the SED fitting is perform without this band.}}
\end{figure*} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed quasars}

@@

% Abstract of the paper
\begin{abstract}
  One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution. Strong lensing magnification effectively increases instrumental resolution and thus addresses this challenge. In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope}(\hst) imaging, using the state-of-the-art \lenstronomy\ code to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models. 
  \mbh\ are estimated from broad emission line using standard methods. Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolves over cosmic time.  At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN. However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and they may become a key diagnostic of black hole and galaxy co-evolution. 
\end{abstract}

@@

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt a the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
The line properties of SDSS1206 have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification. For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015. We derived the line properties from the spectrum using the same approach as~\citep{Sluse2012}. \todo{Dominique and Chris can give more details here.} . The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

@@

{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W. The multi-band imaging data provides us with the opportunity to estimate the host color and improve the stellar mass estimate. We adopted the lensing modelling approach described in Section~\ref{sec:photometry} to infer the host photometry through the F814W and F555W bands. Based on the three band host magnitudes, we find that a 1.5~Gyr age and solar metallicity stellar population provides a good match to the color. More detailed information is presented in Appendix~\ref{app:HE0435}.
%Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy. Thus, we infer the color of the lensed arcs in the image plane. Based a their magnitudes in three bands, we find a 1.5 Gyr stellar population with solar metallicity could well match this color. More detailed information is presented in Appendix~\ref{app:HE0435}.}

@@

\subsection{The \mbh-\mstar\ relation}\label{sec:relation}
In Figures~\ref{fig:scaling_relation}-(a) we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.  We expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget for the entire sample. Following D20, we adopt as baseline a local \mbh-\mstar\ of the form:
\begin{eqnarray}
\label{eq:MMlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}),
  \end {eqnarray}
with  $\alpha = 0.27$, $\beta = 0.98$ based on the local sample of 55 objects measured in a consistent manner. We find that our lensed systems are above the local relation, consistent with the inference from the 32  non-lensed AGNs published by D20 in a  similar redshift range. To quantify the evolution as a function of redshift, we parameterize it as:
\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
\end{eqnarray} 
where the $\Delta \log \mathcal M_{\rm BH}$ is the offset of \mbh\ with respect to the local baseline at fixed \mstar. To make a direct comparison, we reproduce the plot shown in Figure~8 of D20. Then, we add our new lensed AGN measurement and show the result in Figure~\ref{fig:scaling_relation}-(b). We find that the offset from the local relationship is indistinguishable for the two samples. Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain $\gamma=1.49\pm0.43$, which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level. The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the observed value of \mbh\ at a fixed \mstar\ tend to be larger at higher redshift than the ones in the local universe.

The lensed AGN systems analyzed in this work were selected for time delay cosmography work, based on the availability of a time delay and the known detectability of the host galaxy. This is a different selection function that that adopted by D20. It is thus reassuring that the two samples present the same apparent evolution. Naturally, inferring the true underlying evolution requires modeling the selection function (as done by D20), which is not justified given the small sample size of lensed quasars sample. At this stage thus, the lensed quasars should be considered as a check on possible systematic measurements error in the D20 analysis rather than a stand-alone measurement.

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[height=0.45\textwidth]{fig/MBH-Mstar.pdf}}&
{\includegraphics[height=0.45\textwidth]{fig/MBH-Mstar_vz.pdf}}\\
\end{tabular}
\caption{\label{fig:scaling_relation} 
(left): BH masses vs. stellar mass correlation (\mbh-\mstar). The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval of the form given by Equation~\ref{eq:MMlocal}.
(right): Offset of $\log(\mathcal M_{\rm BH})$ at fixed \mstar as a function of redshift. Our new measurements are overlayed on samples of non-lensed AGNs taken from the literature and measured in a self consistent way to facilitate a direct comparison. The red line and shaded region are the best-fit and $1-\sigma$ results of fitting  Equation~\eqref{eq:offset} to the 32 high-z AGNs measured by D20. The blue line and region are the results based on the eight lensed systems presented in this work. The blue and red areas are in agreement within the errors.}
\end{figure*}

@@

We considered a set of modelling choices to perform the fitting and the final inference is based on a weighting of top ranked choices. In particular, we treat the two different modelling approaches, i.e., {\it noise boost} and {\it PSF iteration} equally, to derive the averaged results. Of course, the results are somewhat dependent on the weighting scheme. However, the dependency is smaller than other sources of uncertainty.  For example, the dispersion of the results by the top ranked choices and thus using different weighting schemes would only change the results marginally ($<0.1$~dex).

@@

\section{Conclusions}\label{sec:con}
Using eight strongly lensed AGN systems, we presented a new measurements of the correlations of the mass of supermassive black hole with the stellar masses of their host galaxy. We adopt state-of-the-art lens modelling techniques to estimate the magnitude host galaxy, in terms of a standard \sersic\ profile. We estimated the \mbh\ of our sample using a set of calibrated single-epoch estimators to assure self-consistency and consistency with the comparison samples taken from the literature.

We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the same approache to derive the \mstar\ and calibrated the \mbh\ using consistent recipes. The \mbh-\mstar\ correlation and its evolution with cosmic time is in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}. Thus, the present analysis further strengthens the conclusion of D20, which can be summarized as follows. First, the growth of the supermassive black hole predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift. However, the actual morphologies of these hosts is likely to be more complex, including a disk and bulge component, as in the case of  RXJ1131. In contrast, the galaxies in the local sample are typically bulge-dominated and the bulge mass is adopted as their  \mstar\. Thus, the reported evolution is weaker than what would be inferred by comparing \mbh to bulge \mstar at all redshifts \citep{Bennert++2011}. Taken together, these results are consistent with a scenario in which the stellar mass is transferred from disk to the bulge at a faster rate than the growth of \mbh\ since $z\sim2$.

Our work based on highly magnified AGN showcases the power of strong lensing to effectively increase the resolution of a telescope and shows that uncertainties related to lens modelling are subdominant with respect to other sources of uncertainty like black hole mass. Furthermore, our work provides a powerful verification of the fidelity of the host galaxy reconstruction in non-lensed AGN.

@@

@@

This work is based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. X.D., S.B., and T.T. acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T. \todo{To be updated. Add silverman's grant.}

@@

\subsection{HE0435}\label{app:HE0435}
In addition to WFC3/F160W, HE0435 has been observed through bands ACS/F814W and ACS/F555W (GO-9744; PI: C. S. Kochanek). Our aim is to derive the brightness of the host galaxy through all the three band to investigate the color and stellar population in the image plane. We use the modelling approach introduced in Section~\ref{sec:photometry} to perform this inference for the F814W and F555W bands. To save computer time, we only use the {\it PSF iteration} approach. We also fix the lens mass slope value to 1.9 since it is closer the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}. The inference of the fittings are shown in Figure~\ref{fig:app_HE0435}-(a), (b). Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}} \todo{cite Morishita's paper if any.} to perform the SED fitting. A stellar population with 1.5 Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c). This stellar population is used to estimate the host stellar mass.

\begin{figure*}
\centering
\subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}\\
\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/HE0435_host_color.pdf}}\\
\caption{\label{fig:app_HE0435} 
Illustrations of the inference of HE0435 using the multi-band data. Top two panels: best-fit model of the lensed arcs shown as Figure~\ref{fig:image_inference}. Bottom panel: SED inference. The red points with error bars represent the inferred image plane host flux in the three bands.}
\end{figure*}

@@

\subsection{WFI2033}\label{app:WFI2033}
In addition to WFC3/F160W, WFI2033 has been observed by \hst\ in  four bands, i.e. WFC3/F125W (GO-12874; PI: D. Floyd), WFC3/F140W (GO-13732; PI: A. Nierenberg), ACS/F555W+F814W  (GO-9744; PI: C. S. Kochanek). Similar to Section~\ref{app:HE0435}, the lens modelling and the host photometry of WFI2033 have been inferred through these four bands. The results are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d). Unfortunately, the  F125W data are too shallow to robustly detect the host.  Thus, we does not use the F125W band for the SED fitting. Using four-band photometry, we find a stellar population of 0.625 Gyr age provides a good match to the colors, as shown in Figure~\ref{fig:app_WFI2033}-(e).
\begin{figure*}
\centering
\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/WFI2033_host_color.pdf}}
\caption{\label{fig:app_WFI2033} 
Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. The F125W dare are too shallow to detect the host and are thus omitted in the fit.}
\end{figure*} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
